\textbf{Introduction, background to research, overview of research, aims and objectives, terms of reference, key research questions}

\begin{itemize}
	\item The Main Text area is the section that contains your fully formed thesis and it is the section where the 8,000-word limit applies.
	Your Report, irrespective of the nature of the topic, must contain critical comment based on the considered assessment of the material/evidence presented in it: this is an essential requirement, as are the conclusions of the report.
	\item Your Report will not be made available to the general public by any means of distribution and, accordingly, you do not need to worry about getting permission from copyright holders in making direct quotations or copying figures from other publications. However, your sources must be acknowledged. You must also indicate by the use of inverted commas or different typeface the quoted material so that it is clearly identified as such. However, if you subsequently write up your work, in conjunction with your Supervisor, as a paper, then you are subject to normal copyright laws and must only quote very brief extracts even from those Journals, which subscribe to the Royal Society's convention on Fair Copying.
	\item Depending on the nature of the report, the main text should start with a review of previous literature. In a review and discussion of the work of others (and at all times) it should be clear from the text which of the opinions expressed are those of the author and which are those of other people.
	\item Where appropriate, students can include links to electronic/video material created in support of and as part of the IRR.
	
	
	
\end{itemize}

Your final Report should be no longer than 8,000 words. The word limit applies to the main text area only, as this is where your report is introduced and then carried forward. Your final word-count should not include: title page, synopsis, acknowledgements, list of contents, notation (if applicable), references, bibliography or appendix/appendices. Shorter Reports are allowed depending on the nature of the research (for example some mathematical and statistical projects are usually shorter than qualitative projects). Reports longer than 8,000 words will be penalised.\\
\\
If the Report is to contain a considerable number of tables and figures, it may be best to place them in an appendix and use in the main text only such summary tables or charts as will assist the reader in following your arguments without necessarily having to go into great detail. This may help to ensure a smooth and uninterrupted presentation.\\
\\
5.11 UNACCEPTABLE PRESENTATION
\textbf{Examiners will not accept projects where the presentational guidelines are not adhered to}. They will not accept projects that have any of the following:
Copyright statements (in any format including as a header/footer);
Confidentiality statements (in any format including as a header/footer);
Non standard font size, type and line spacing;
Page numbers missing;
No contents pages or contents pages with no page numbers indicated.


